### 2016-03-21 manuscript.Rnw
add paragraphs about gol and collection endpoints

\texttt{rotl} gives users access to all endpoints provided by version 2 of the
OTL APIs, and other versions of the API can be selected by the user as they
become available. Phylogenetic trees served by the API can be imported directly into
R's memory and are represented using the \texttt{ape} \citep{Paradis2004} tree
structure (objects of class \texttt{phylo}), or can be written to files in the
Newick, NEXUS \citep{Maddison1997}, or NeXML \citep{Vos2012} file formats. This
allows researchers to use these trees either directly with other R packages, or
to be imported in other programs that make use of phylogenetic tree files.

>>>>

\texttt{rotl} gives users access to the endpoints provided by version 2 of the
APIs, and other versions of the APIs can be selected by the user as they become
available (version 3 is scheduled to be released at the end of March 2016). Two
other end-points are available in version 2 of the API: \emph{graph of life} and
\emph{collections}. Data from the \emph{graph of life} endpoint are not intended
for typical users, and will be removed in future releases. The \emph{collection}
endpoint is not fully functional, and no functions are available in the current
release of \texttt{rotl}. Future versions will make them available when the API
implements them.

Phylogenetic trees served by the API can be imported directly into R's
memory and are represented using the \texttt{ape} \citep{Paradis2004} tree
structure (objects of class \texttt{phylo}), or can be written to files in the
Newick, NEXUS \citep{Maddison1997}, or NeXML \citep{Vos2012} file formats. This
allows researchers to use these trees either directly with other R packages, or
to be imported in other programs that make use of phylogenetic tree files.
